HaPy \\ Haskell for Python

### 2011-12-17 paper.tex
full outline

\section{Use}

\subsection{Loading Haskell Modules}
% - super easy: all haskell modules represented as submodules of HaPy
% - import HaPy.Data.List

@@

@@

@@

@@

\section{Future work}
In future, HaPy could support dynamic conversion from ADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type.

\section{Refernces}
System.Plugins stuff.

>>>>

\section{Use}
% - Meshing python and haskell semantics

\subsection{Loading Haskell Modules}
% - super easy: all haskell modules represented as submodules of HaPy
%  - standard haskell module represnetnation (e.x. System.Plugins) preserved
% - import HaPy.Data.List

@@

% - Split across three languages
%  - to our surprise currently very little in C
%  - choice of what language to work in for each feature
% - Python side uses Ctypes to dynamically load our precompiled C and Haskell shared object file 
%  - idea: in future statily compile C-python module

@@

% - hs-plugins

@@

% C interface supports applying one argument at a time for each of

@@

% David

\section{Future work}

% real type checking

\subsection{Supporting more types}

% marshalling lists
% mashralling ADTs

\subsection{Improved dynamic loading}

% 64-bit bug
% difficultly in loading preinstalled modules
%  - plugins only supports very simply model (like assuming that .hi file is next to .o file)
% requires dynamic libraries

\subsection{Simplied install}

% require user of compiled binary to have dynamically compiled binary of haskell libraries

\subsection{Passing Python Callbacks}

\section{Refernces}

% hs-plugins 
% missing py?
